% \bibitem{system-o}Odersky, M., Wadler, P. \& Wehr, M. A Second Look at Overloading. 
% {\em Proceedings Of The Seventh International Conference On Functional Programming Languages And Computer Architecture}. 
% pp. 135-146 (1995), https://doi.org/10.1145/224164.224195
% \bibitem{hindley-milner}Milner, R. A theory of type polymorphism in programming. 
% {\em Journal Of Computer And System Sciences}. 
% \textbf{17}, 348-375 (1978), https://www.sciencedirect.com/science/article/pii/0022000078900144
% - https://dl.acm.org/doi/pdf/10.1145/227699.227700
% - https://link.springer.com/chapter/10.1007/3-540-19027-9_9
% - https://www.ioc.ee/~cneste/files/system-f-fun-and-profit.pdf
% - https://dl.acm.org/doi/pdf/10.1145/582153.582176
% - https://www.microsoft.com/en-us/research/wp-content/uploads/1997/01/henk.pdf
% - https://dl.acm.org/doi/10.5555/207528
% - https://www4.di.uminho.pt/~mjf/pub/PSVC-Lecture7.pdf

\bibitem{agda} Bove, A., Dybjer, P., Norell, U. (2009). A Brief Overview of Agda – A Functional Language with Dependent Types. In: Berghofer, S., Nipkow, T., Urban, C., Wenzel, M. (eds) Theorem Proving in Higher Order Logics. TPHOLs 2009. Lecture Notes in Computer Science, vol 5674. Springer, Berlin, Heidelberg. \url{https://doi.org/10.1007/978-3-642-03359-9_6}

\bibitem{itt} Martin-Löf, P. \& Sambin, G. Intuitionistic Type Theory. (Bibliopolis, 1984), \url{https://www.cse.chalmers.se/~peterd/papers/MartinL%C3%B6f1984.pdf}

\bibitem{pts} Barendregt, H. Introduction to generalized type systems. {\em Journal Of Functional Programming}. \textbf{1}, 125-154 (1991), \url{https://doi.org/10.1017%2Fs0956796800020025}

\bibitem{hm} Milner, R. A theory of type polymorphism in programming. 
{\em Journal Of Computer And System Sciences}. 
\textbf{17}, 348-375 (1978), \url{https://www.sciencedirect.com/science/article/pii/0022000078900144}


\bibitem{syso} Odersky, M., Wadler, P. \& Wehr, M. A Second Look at Overloading. 
{\em Proceedings Of The Seventh International Conference On Functional Programming Languages And Computer Architecture}. 
pp. 135-146 (1995), \url{https://doi.org/10.1145/224164.224195}

\bibitem{logrel}ABEL, A., ALLAIS, G., HAMEER, A., PIENTKA, B., MOMIGLIANO, A., SCHÄFER, S. \& STARK, K. POPLMark reloaded: Mechanizing proofs by logical relations. {\em Journal Of Functional Programming}. \textbf{29} pp. e19 (2019), \url{http://dx.doi.org/10.1017/S0956796819000170}

\bibitem{code} Weidner, M. Affiliated Agda code. (GitHub, 2023). \url{https://github.com/Mari-W/System-Fo/tree/main/proofs}
